---
title: "PUBG Weapon"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

Loading the dataset to r
```{r}
PUBG <- read.csv("PUBGweapon.csv")
PUBG
```

Checking the overview of the dataset
```{r}
str(PUBG)
```
The dataset has 20 variables and 44 observations.


Scatterplot of bullet speed of each weapon
```{r}
ggplot(PUBG, aes(x = Weapon.Name, y = Bullet.Speed, color = x)) +
  geom_point(colour = "bisque4")

Best_BS <- PUBG%>%
  filter(Bullet.Speed >= 600)

str(Best_BS)

ggplot(Best_BS, aes(x = Weapon.Name, y = Bullet.Speed)) +
   geom_point(colour = "bisque4")
```


Checking on correlation and coefficients between Range and Damage possible of the 21 weapons.
```{r}
lm_dmgrng <- lm(Damage ~ Range, data = Best_BS)
lm_dmgrng
summary(lm_dmgrng)
cor(Best_BS$Damage, Best_BS$Range)

Best_BS%>%
  ggplot(aes(x=Range, y=Damage)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```


BDMG(Body Damage) and Range Comparison
```{r}
Best_BS%>%
  ggplot(aes(x=Range, y=BDMG_0, color = Weapon.Name)) +
  geom_point() 

Best_BS%>%
  ggplot(aes(x=Range, y=BDMG_1, color = Weapon.Name)) +
  geom_point() 

Best_BS%>%
  ggplot(aes(x=Range, y=BDMG_2, color = Weapon.Name)) +
  geom_point() 

Best_BS%>%
  ggplot(aes(x=Range, y=BDMG_3, color = Weapon.Name)) +
  geom_point()
```


HDMG(Head Damage) and Range Comparison
```{r}
Best_BS%>%
  ggplot(aes(x=Range, y=HDMG_0, color = Weapon.Name)) +
  geom_point() 

Best_BS%>%
  ggplot(aes(x=Range, y=HDMG_1, color = Weapon.Name)) +
  geom_point() 

Best_BS%>%
  ggplot(aes(x=Range, y=HDMG_2, color = Weapon.Name)) +
  geom_point()

Best_BS%>%
  ggplot(aes(x=Range, y=HDMG_3, color = Weapon.Name)) +
  geom_point()
```


Filtering it down, out of the 21 weapons with best bullet speed to best damages.
```{r}
Best_BS_DMG <- Best_BS%>%
  filter(HDMG_3 > 60, BDMG_3 > 30 )

Best_BS_DMG
```







